% ============================================================
%  Order Flow & Technical Indicator Predictability
%  Full IMRD Research Paper — orderflow-rs Series P4–P7
% ============================================================
\documentclass[12pt,a4paper]{article}

% ── Core typography ───────────────────────────────────────────────────────────
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}           % character protrusion & font expansion

% ── Page layout ──────────────────────────────────────────────────────────────
\usepackage[top=2.8cm,bottom=2.8cm,left=3cm,right=3cm,headheight=14pt]{geometry}
\usepackage{setspace}
\onehalfspacing

% ── Mathematics ──────────────────────────────────────────────────────────────
\usepackage{amsmath,amssymb,amsthm}
\usepackage{bm}                  % bold math

% ── Tables ───────────────────────────────────────────────────────────────────
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{makecell}
\usepackage{ragged2e}
\usepackage[table]{xcolor}

% ── Figures ──────────────────────────────────────────────────────────────────
\usepackage{graphicx}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\captionsetup{font=small,labelfont=bf}

% ── Colour ───────────────────────────────────────────────────────────────────
\definecolor{darkblue}{RGB}{0,40,85}
\definecolor{medblue}{RGB}{20,80,160}
\definecolor{lightblue}{RGB}{220,232,248}
\definecolor{accent}{RGB}{180,30,30}
\definecolor{green1}{RGB}{20,120,60}
\definecolor{gray1}{RGB}{100,100,100}
\definecolor{rowgray}{RGB}{248,248,250}

% ── Headers & footers ────────────────────────────────────────────────────────
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\lhead{\textcolor{gray1}{\small\textit{orderflow-rs Research Series}}}
\rhead{\textcolor{gray1}{\small\textit{P4--P7: LOB Predictability}}}
\cfoot{\textcolor{gray1}{\small\thepage}}
\renewcommand{\headrulewidth}{0.3pt}
\renewcommand{\headrule}{\color{medblue}\hrule width\headwidth height\headrulewidth}

% ── Section headings ─────────────────────────────────────────────────────────
\usepackage{titlesec}
\titleformat{\section}
  {\large\bfseries\color{darkblue}}
  {\colorbox{lightblue}{\,\thesection\,}}{0.8em}{}
  [\vspace{-0.3em}{\color{medblue}\hrule height 0.8pt}\vspace{0.3em}]

\titleformat{\subsection}
  {\normalsize\bfseries\color{darkblue}}
  {\thesubsection}{0.8em}{}

\titleformat{\subsubsection}
  {\normalsize\itshape\color{medblue}}
  {\thesubsubsection}{0.8em}{}

\titlespacing*{\section}{0pt}{14pt}{6pt}
\titlespacing*{\subsection}{0pt}{10pt}{4pt}

% ── Boxes & callouts ─────────────────────────────────────────────────────────
\usepackage{tcolorbox}
\tcbuselibrary{skins,breakable}

\newtcolorbox{findingbox}[1][]{
  enhanced, breakable,
  colback=lightblue!60,
  colframe=medblue,
  fonttitle=\bfseries\small\color{darkblue},
  title={#1},
  left=4pt, right=4pt, top=4pt, bottom=4pt,
  boxrule=0.6pt,
  arc=3pt,
}

\newtcolorbox{keyresult}{
  enhanced,
  colback=green1!8,
  colframe=green1,
  left=4pt, right=4pt, top=4pt, bottom=4pt,
  boxrule=0.6pt,
  arc=3pt,
  fontupper=\small,
}

\newtcolorbox{warningbox}{
  enhanced,
  colback=accent!8,
  colframe=accent,
  left=4pt, right=4pt, top=4pt, bottom=4pt,
  boxrule=0.6pt,
  arc=3pt,
  fontupper=\small,
}

% ── Lists ────────────────────────────────────────────────────────────────────
\usepackage{enumitem}
\setlist[itemize]{leftmargin=1.5em,itemsep=2pt,parsep=0pt}
\setlist[enumerate]{leftmargin=1.8em,itemsep=2pt,parsep=0pt}

% ── Footnotes ────────────────────────────────────────────────────────────────
\usepackage[hang,flushmargin]{footmisc}

% ── Hyperlinks ───────────────────────────────────────────────────────────────
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  linkcolor=darkblue,
  citecolor=medblue,
  urlcolor=medblue,
  pdftitle={Order Flow and Technical Indicator Predictability in LOB Data},
  pdfsubject={Quantitative Finance, Market Microstructure},
  pdfkeywords={limit order book, information coefficient, mean reversion,
    cryptocurrency, foreign exchange, technical analysis},
}

% ── Bibliography ─────────────────────────────────────────────────────────────
\usepackage{natbib}
\bibliographystyle{plainnat}

% ── Plots ────────────────────────────────────────────────────────────────────
\usepackage{pgfplots}
\pgfplotsset{compat=1.18,
  every axis/.append style={
    font=\small,
    grid=both,
    grid style={line width=0.2pt,draw=gray!25},
  }
}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning,shapes,fit,calc}

% ── Theorem environments ─────────────────────────────────────────────────────
\newtheorem{hypothesis}{Hypothesis}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\theoremstyle{remark}
\newtheorem{remark}{Remark}[section]

% ── Custom macros ─────────────────────────────────────────────────────────────
\newcommand{\IC}{\mathrm{IC}}
\newcommand{\OFI}{\mathrm{OFI}}
\newcommand{\code}[1]{\texttt{\small #1}}
\newcommand{\pos}[1]{\textcolor{green1}{\textbf{+#1}}}
\newcommand{\negval}[1]{\textcolor{accent}{\textbf{$-$#1}}}
\newcommand{\sectionlabel}[1]{%
  \begin{center}
    \colorbox{darkblue}{\color{white}\bfseries\large\quad #1 \quad}
  \end{center}
  \vspace{4pt}
}

% ── parskip ──────────────────────────────────────────────────────────────────
\usepackage[parfill]{parskip}
\emergencystretch=2em
\setlength{\parskip}{6pt}

% =============================================================================
\begin{document}
% =============================================================================

% ── Title page ───────────────────────────────────────────────────────────────
\begin{titlepage}
\centering
\vspace*{1.2cm}

{\color{darkblue}\rule{\linewidth}{3pt}}
\vspace{0.8cm}

{\LARGE\bfseries\color{darkblue}
Order Flow and Technical Indicator Predictability\\[0.4cm]
in High-Frequency Limit Order Book Data}

\vspace{0.5cm}
{\color{medblue}\rule{0.6\linewidth}{1pt}}
\vspace{0.5cm}

{\large\itshape\color{gray1}
A Cross-Asset Empirical Study of Cryptocurrency,\\
Foreign Exchange, and Synthetic Market Microstructure}

\vspace{1.8cm}

{\large\bfseries Evint Leovonzko}

\vspace{1.0cm}
{\color{medblue}\rule{0.4\linewidth}{0.5pt}}
\vspace{0.6cm}

{\normalsize April 2025}

\vfill
\begin{tcolorbox}[
  enhanced,
  colback=rowgray,
  colframe=gray1!50,
  arc=3pt,
  boxrule=0.4pt,
  width=0.90\linewidth,
  center,
]
\small\color{gray1}
\textbf{Codebase:}
\href{https://github.com/Evintkoo/orderflow-rs}{\texttt{github.com/Evintkoo/orderflow-rs}}
(Rust, 210 tests passing)
\quad\textbullet\quad
\textbf{Reproducibility:} \code{cargo run --release -{}- techanalysis data/ reports/}
\end{tcolorbox}
\end{titlepage}

% ── Declaration of Originality ────────────────────────────────────────────────
\thispagestyle{empty}
\vspace*{2cm}

{\large\bfseries\color{darkblue} Declaration of Originality}

\vspace{0.8cm}

I hereby declare that this work is my own original research and has not
been submitted elsewhere for publication in the same form.
All sources consulted are acknowledged in the references. The
\code{orderflow-rs} codebase, data collection pipeline, and all
empirical analyses reported herein were designed and implemented by
the author.

\vspace{1.5cm}
\noindent
\begin{tabular}{ll}
Signature: & \underline{\hspace{6cm}} \\[0.8cm]
Date:       & \underline{\hspace{6cm}} \\
\end{tabular}

\vfill
\noindent{\small\color{gray1}
Word count (excluding tables, figures, and appendices): approximately 8{,}500 words.}

\newpage

% ── Abstract ─────────────────────────────────────────────────────────────────
\thispagestyle{empty}
\begin{center}
{\large\bfseries\color{darkblue} Abstract}
\end{center}

\vspace{0.4cm}

This thesis presents a four-phase empirical study of return predictability
at limit order book (LOB) snapshot frequency, covering 187 symbol--source
files (162 unique instrument--source pairs) across foreign exchange (FX),
cryptocurrency, and mixed-asset markets. The study proceeds from a
validated synthetic LOB simulator (\textbf{Phase P4}) through direct
statistical testing on approximately 85 million real LOB snapshots
(\textbf{Phase P5}), a walk-forward backtest with explicit transaction
costs (\textbf{Phase P6}), and a systematic information coefficient (IC)
evaluation of 87 technical indicators at four return horizons
(\textbf{Phase P7}). All analyses are implemented in a reproducible
open-source Rust pipeline (\href{https://github.com/Evintkoo/orderflow-rs}
{\texttt{github.com/Evintkoo/orderflow-rs}}, 210 passing tests).

\medskip
\textbf{Principal findings:}
\begin{enumerate}[leftmargin=1.8em,itemsep=3pt]
  \item Cryptocurrency spot markets exhibit strong sub-minute
    mean-reversion: Spearman $\IC_{5\text{s}} = 0.24$--$0.48$ for
    z-score and pivot-distance indicators, consistent across six
    independent exchanges covering 85 WebSocket-sampled instruments.
  \item Foreign exchange spot markets show statistically negligible
    technical predictability across all 87 indicators at $\sim$1\,s
    LOB resolution, consistent with efficient institutional
    market-making eliminating sub-minute patterns.
  \item Mean-reversion signals in cryptocurrency markets have a
    half-life well below 60 seconds: identical instruments sampled
    at $\approx 0.3$\,s (WebSocket) yield positive IC whereas the
    same instruments sampled at 60\,s (REST API) yield sign-reversed IC,
    implying that data-acquisition frequency determines signal direction.
  \item Walk-forward OLS backtests on FX yield uniformly negative net
    profit-and-loss at all tested thresholds, establishing that the
    observed FX IC of 0.02--0.04 is economically insufficient to
    overcome standard execution costs.
\end{enumerate}

\vspace{0.5cm}
\noindent\textbf{Keywords:} limit order book; information coefficient;
market microstructure; mean reversion; cryptocurrency; foreign exchange;
technical analysis; high-frequency trading; order-flow imbalance;
Spearman rank correlation.

\vspace{0.3cm}
\noindent\textbf{JEL Classification:}
G12 (Asset pricing);
G14 (Information and market efficiency);
G15 (International financial markets);
C58 (Financial econometrics).

\newpage

% ── Table of contents ────────────────────────────────────────────────────────
\renewcommand{\contentsname}{\color{darkblue}Table of Contents}
\tableofcontents
\newpage

% =============================================================================
\sectionlabel{INTRODUCTION}
% =============================================================================

\section{Introduction}
\label{sec:intro}

\subsection{Background and Motivation}

The limit order book (LOB) --- the real-time record of all outstanding
buy and sell orders at each price level --- is the primary mechanism
through which price discovery occurs in modern electronic markets.
At millisecond to second timescales, the LOB encodes the collective
information of all active market participants: their willingness to
buy, their willingness to sell, and the dynamics of how both sides
of the market evolve in response to new information.

A natural question in quantitative finance is whether the structure of
the LOB at time $t$ contains exploitable information about the direction
of price movement over the next few seconds or minutes. Positive evidence
would have profound implications for the design of execution algorithms,
market-making strategies, and directional trading systems.

\subsection{Existing Literature}

The empirical literature on LOB predictability spans three broad strands:

\paragraph{Order-flow imbalance (OFI).}
\citet{cont2014price} demonstrated that the net signed change in bid
and ask depth at the best quote (OFI) predicts five-minute returns in
equity markets with Spearman IC of 0.15--0.25. Subsequent work by
\citet{zarinelli2015beyond} documented the concavity of market impact
and the role of deeper book levels. These findings motivate the OFI
features used throughout this study.

\paragraph{FX microstructure.}
\citet{evans2002order} established that order flow is the primary driver
of daily exchange rate changes in interdealer FX markets. Less is known
about sub-minute, tick-level predictability in FX, particularly because
high-frequency LOB data from FX markets has been less accessible to
academic researchers than exchange-reported equity data.

\paragraph{Cryptocurrency microstructure.}
The cryptocurrency microstructure literature is comparatively recent.
\citet{makarov2020trading} document large, persistent price deviations
across crypto exchanges, indicating significant limits to arbitrage.
Several exchange-specific studies find strong and persistent
intraday predictability, plausibly attributable to the combination of
high retail participation, 24/7 continuous trading, and the absence of
designated market-maker obligations that characterise institutional
FX and equity venues \citep{bianchi2022trading}.

\paragraph{Market microstructure theory.}
The theoretical foundation for LOB predictability rests on adverse
selection models. \citet{kyle1985} showed that informed
traders reveal information gradually through order flow, creating
price impact and transient predictability. \citet{glosten1985}
derived bid-ask spreads from adverse selection costs.
\citet{madhavan2000market} provides a comprehensive survey of the
empirical literature arising from these models. The statistical
properties of LOB price processes are studied in \citet{bouchaud2002statistical},
who find that order-book dynamics exhibit long-memory and power-law
distributions, motivating the use of statistical indicators in the
present study.

\paragraph{Technical indicators at high frequency.}
Classical technical analysis indicators --- RSI, MACD, Bollinger Bands,
and the like --- were developed for daily or weekly bar data. Whether
they carry predictive power at sub-minute LOB frequency has received
little systematic treatment in the academic literature.
\citet{lo2000foundations} provide partial empirical support for
technical analysis at daily frequency using non-parametric kernel
methods, but do not extend the analysis to intraday data.
The present study fills this gap through a systematic IC evaluation
at LOB-snapshot frequency, which constitutes the central contribution
of Phase~P7.

\subsection{Research Questions}

This study addresses four interconnected questions:

\begin{enumerate}
  \item \textbf{(P4)} Can a synthetic LOB simulator with a three-agent
    population correctly reproduce the statistical properties of
    order-flow features?
  \item \textbf{(P5)} Which microstructure features carry statistically
    significant predictive IC in real FX LOB data, and at what horizon?
  \item \textbf{(P6)} Does the observed statistical predictability in FX
    translate into net-positive trading performance after realistic
    transaction costs?
  \item \textbf{(P7)} Which of 87 classical and microstructure-inspired
    technical indicators carry predictive IC across asset classes, and
    how does that IC vary with sampling frequency and asset class?
\end{enumerate}

\subsection{Contributions}

This thesis makes five specific contributions to the literature:

\begin{enumerate}
  \item A fully validated, open-source Rust LOB simulator with
    Ornstein-Uhlenbeck price dynamics, Hawkes arrival processes, and
    a three-agent population, including documented resolutions of
    four non-obvious implementation bugs.
  \item The first systematic IC evaluation of 87 technical indicators
    at LOB-snapshot frequency across 187 symbol--source files spanning
    15 data providers and three asset classes.
  \item A cross-asset comparison (FX vs.\ cryptocurrency vs.\ mixed)
    that isolates market microstructure regime differences with
    unusually large sample sizes ($\sim$85 million LOB snapshots).
  \item An empirical demonstration of the frequency-sensitivity of
    mean-reversion signals: identical instruments sampled at 0.3\,s
    vs.\ 60\,s yield opposite-signed IC.
  \item A quantified IC hurdle rate for sub-minute strategies based on
    a walk-forward backtest with explicit cost modelling.
\end{enumerate}

\subsection{Thesis Organisation}

The remainder of this thesis is structured as follows.
Chapter~\ref{sec:methods} (\textbf{Methods}) covers data acquisition,
the LOB feature pipeline, the synthetic simulation design, the
walk-forward backtest methodology, and the statistical IC framework.
Chapter~\ref{sec:results} (\textbf{Results}) reports all empirical
findings for each phase without interpretation, presenting tables
and figures in a self-contained manner.
Chapter~\ref{sec:discussion} (\textbf{Discussion}) interprets the
results, identifies the underlying microstructure mechanisms, draws
practical implications for strategy design, and acknowledges
limitations.
Chapter~\ref{sec:conclusion} states the principal conclusions and
outlines directions for future research (Phase~P8).
The appendices contain the full 87-indicator IC ranking table and
reproducibility instructions for replicating every result from
the open-source codebase.

% =============================================================================
\newpage
\sectionlabel{METHODS}
% =============================================================================

\section{Methods}
\label{sec:methods}

\subsection{Overview of the Four-Phase Pipeline}
\label{sec:pipeline_overview}

The study is organised as a sequential pipeline, with each phase
building on the validated outputs of the previous one.
Figure~\ref{fig:pipeline} illustrates the flow.

\begin{figure}[H]
\centering
\resizebox{\linewidth}{!}{%
\begin{tikzpicture}[
  node distance=1.4cm,
  box/.style={rectangle,rounded corners=4pt,draw=darkblue,
    fill=lightblue!60,minimum width=3.8cm,minimum height=1.1cm,
    text width=3.6cm,align=center,font=\small\bfseries},
  arrow/.style={-{Stealth[length=6pt]},thick,color=medblue},
  label/.style={font=\footnotesize\itshape,color=gray1,align=center},
]
\node[box] (P4) {P4\\Synthetic Simulation};
\node[box,right=1.6cm of P4] (P5) {P5\\FX IC Testing};
\node[box,right=1.6cm of P5] (P6) {P6\\Backtest};
\node[box,right=1.6cm of P6] (P7) {P7\\Tech.\ IC\\(87 indicators)};

\draw[arrow] (P4) -- node[above,label]{Pipeline\\validation} (P5);
\draw[arrow] (P5) -- node[above,label]{Signal\\selection} (P6);
\draw[arrow] (P6) -- node[above,label]{Cost\\calibration} (P7);

\node[below=0.4cm of P4,label] {OU+Hawkes\\2.88\,M rows};
\node[below=0.4cm of P5,label] {Dukascopy FX\\24\,M rows};
\node[below=0.4cm of P6,label] {Walk-forward\\OLS};
\node[below=0.4cm of P7,label] {162 symbols\\85\,M rows};
\end{tikzpicture}%
}
\caption{Four-phase research pipeline. Each phase uses the validated
outputs of the previous phase.}
\label{fig:pipeline}
\end{figure}

\subsection{Data Acquisition}
\label{sec:data}

\subsubsection{Data Sources and Coverage}

LOB data were collected from 15 sources spanning three asset classes.
Table~\ref{tab:datasources} provides a complete inventory of all
sources with non-empty data. Equity-specific providers (Alpaca,
Polygon, Finnhub, Tiingo) are included in the pipeline but produced
empty feature files for the analysis period and are excluded from
quantitative results. The study covers 162 unique instrument--source
pairs in total; the Phase~P7 IC analysis operates on 187 feature
files (the discrepancy arises because certain instruments appear
under slightly different symbol identifiers across sub-feeds of
the same exchange).

\begin{table}[H]
\centering
\caption{Data sources with non-empty feature files. $\bar{\Delta t}$ is
the average time between consecutive LOB snapshots. ``Rows/sym.''
is the approximate row count per symbol.}
\label{tab:datasources}
\small
\setlength{\tabcolsep}{5pt}
\begin{tabular}{lllrr}
\toprule
\textbf{Source} & \textbf{Feed type} & \textbf{Asset class}
  & $\bar{\Delta t}$ & \textbf{Rows/sym.} \\
\midrule
Binance         & WebSocket   & Crypto    & 0.29\,s   & $\sim$323\,k \\
Bybit           & WebSocket   & Crypto    & $\sim$0.30\,s & $\sim$204\,k \\
Coinbase        & WebSocket   & Crypto    & 0.05\,s   & $\sim$3.2\,M \\
OKX             & WebSocket   & Crypto    & $\sim$0.30\,s & $\sim$469\,k \\
Bitstamp        & WebSocket   & Crypto    & $\sim$0.30\,s & $\sim$53\,k \\
Gemini          & WebSocket   & Crypto    & $\sim$0.30\,s & $\sim$1.5\,M \\
Binance         & REST (1\,min) & Crypto  & 60.0\,s   & $\sim$44\,k \\
Dukascopy       & Tick (hist.) & FX spot  & 0.97\,s   & $\sim$2.4\,M \\
Yahoo Finance   & Daily/intraday & Mixed  & varies    & $\sim$15\,k \\
Synthetic (sim.)& In-memory   & Simulation & 0.10\,s & 2.88\,M \\
\bottomrule
\multicolumn{5}{l}{\small\itshape Total LOB snapshot rows across all
  sources: approximately 85 million.}
\end{tabular}
\end{table}

\subsubsection{Instruments Covered}

\begin{itemize}
  \item \textbf{Cryptocurrency (9 exchanges, 85 symbol--source pairs):}
    BTC, ETH, SOL, XRP, ADA, AVAX, DOGE, DOT, LINK, LTC (USDT or
    USD quote currency depending on exchange).
  \item \textbf{FX spot (Dukascopy, 10 pairs):} EUR/USD, GBP/USD,
    USD/JPY, USD/CHF, AUD/USD, NZD/USD, USD/CAD, EUR/GBP, EUR/JPY,
    GBP/JPY.
  \item \textbf{Mixed (Yahoo Finance, 48 symbols):} Large-cap equities
    (AAPL, MSFT, NVDA, \ldots), ETFs (SPY, QQQ, TLT, \ldots),
    indices (S\&P 500, DJIA, VIX), commodities futures (GC, CL, NG),
    and crypto/FX cross-rates.
\end{itemize}

\subsection{LOB Feature Engineering}
\label{sec:features}

\subsubsection{Feature Extraction Pipeline}

Each LOB snapshot is processed by a stateful feature extractor
(\code{src/\allowbreak features/\allowbreak mod.rs}) that maintains rolling state across
snapshots for the same instrument. Eleven features are computed
per snapshot:

\begin{equation}
\mathbf{f}_t = \bigl[
  \underbrace{\OFI_1,\;\OFI_5,\;\OFI_{10}}_{\text{order-flow}},\;
  \underbrace{\delta_\mathrm{depth},\;\mu_\mathrm{micro},\;q_\mathrm{imb}}_{\text{queue/price}},\;
  \underbrace{\sigma,\;\lambda_\mathrm{trade},\;\kappa_\mathrm{impact}}_{\text{activity}},\;
  \underbrace{\ell_\mathrm{drain},\;w_\mathrm{slope}}_{\text{book shape}}
\bigr]
\label{eq:features}
\end{equation}

\begin{definition}[Order-Flow Imbalance]
The $k$-level order-flow imbalance is defined as:
\begin{equation}
  \OFI_k = \sum_{i=1}^{k}\bigl(\Delta Q^b_i - \Delta Q^a_i\bigr)
\end{equation}
where $\Delta Q^b_i$ ($\Delta Q^a_i$) is the signed change in quantity
at the $i$-th bid (ask) level between consecutive snapshots. Positive
$\OFI$ indicates net buying pressure.
\end{definition}

Remaining features: $\delta_\mathrm{depth}$ = depth imbalance
(bid depth minus ask depth normalised by total depth);
$\mu_\mathrm{micro}$ = microprice deviation from mid-price;
$q_\mathrm{imb}$ = queue imbalance at the best bid/ask;
$\sigma$ = quoted bid-ask spread;
$\lambda_\mathrm{trade}$ = trade arrival rate (trades per second);
$\kappa_\mathrm{impact}$ = estimated price impact coefficient;
$\ell_\mathrm{drain}$ = level drain indicator (speed at which depth is
consumed); $w_\mathrm{slope}$ = weighted mid-price slope over the last
$n$ snapshots.

\subsubsection{Return Label Construction}

Four non-overlapping log-return horizons are used,
$\tau \in \{1, 5, 30, 300\}$\,s:
\begin{equation}
  r_\tau(t) = \log\!\left(\frac{p_{t+\tau}}{p_t}\right)
\label{eq:returns}
\end{equation}
These are stored as columns \code{r\_1s}, \code{r\_5s},
\code{r\_30s}, \code{r\_300s} in the feature CSV.
The use of non-overlapping returns is critical for unbiased IC
estimation (see Section~\ref{sec:backtest_design}).

\subsection{Technical Indicator Construction (Phase P7)}
\label{sec:techind_methods}

\subsubsection{Price Index Reconstruction}

Because the feature pipeline stores returns rather than absolute prices,
a normalised price index is reconstructed for indicator computation:
\begin{equation}
  p_0 = 1.0,\qquad
  p_{i+1} = p_i \cdot \bigl(1 + 0.1\,r_{1\mathrm{s},i}\bigr)
\label{eq:priceindex}
\end{equation}
The scalar 0.1 attenuates volatility to a scale comparable to daily
prices, preventing numerical overflow in long-window moving averages.
High and low approximations use the contemporaneous spread $\sigma_t$:
\begin{equation}
  h_t = p_t + \tfrac{1}{2}\sigma_t,\qquad
  l_t = \max\!\bigl(p_t - \tfrac{1}{2}\sigma_t,\;10^{-10}\bigr)
\end{equation}
Volume is proxied by trade intensity $\lambda_\mathrm{trade}$.

\subsubsection{Indicator Library}

Eighty-seven indicators are organised into eight categories.
Table~\ref{tab:indcats} lists each category with representative members.
All indicators are implemented as pure, stateless functions
$\mathbb{R}^n \to \mathbb{R}^n$ in \code{src/analysis/techind.rs};
positions where the warm-up window is not yet satisfied are returned
as \texttt{None}.

\begin{table}[H]
\centering
\caption{Technical indicator categories, counts, and examples.}
\label{tab:indcats}
\small
\begin{tabular}{ll>{\RaggedRight\arraybackslash}p{8cm}}
\toprule
\textbf{Category} & \textbf{Count} & \textbf{Examples} \\
\midrule
Moving Averages     & 13 &
  SMA(10/20/50/100/200), EMA(5/12/20/26/50/200), WMA(14),
  HMA(14), KAMA(10), DEMA(20), TEMA(20) \\
Trend               & 10 &
  ADX(14), DI$+$(14), DI$-$(14), Aroon Up/Down(25),
  Choppiness(14), Supertrend(14), Golden/Death Cross \\
Momentum            & 14 &
  RSI(7/14/21), Stoch \%K(14)/\%D(14), Williams \%R(14),
  CCI(20), CMO(14), ROC(10/20), Momentum(10/20),
  MACD line/signal/histogram, Awesome Oscillator, DPO(20) \\
Volatility          & 11 &
  Bollinger \%B(20)/Width(20), ATR(14), NATR(14),
  Keltner Width(20), Parkinson Vol(14), Garman-Klass(20),
  Realised Vol(20), Squeeze Signal \\
Volume              & 7  &
  OBV, VPT, MFI(14), Force Index(13), RVOL(20), VROC(14),
  Ease of Movement(14) \\
Support/Resistance  & 6  &
  Pivot Distance, R1 Distance, S1 Distance,
  Fibonacci 0.618 Distance, Donchian Width(20),
  High/Low Distance(20/50) \\
Statistical         & 10 &
  Z-Score(10/20/50), Autocorrelation(lag 1/5), Hurst(100),
  Variance Ratio(16), LR Slope(20), LR Deviation(20), LR R$^2$(20) \\
Microstructure      & 9  &
  VWAP Deviation, Book Pressure, Effective Spread,
  Spread Change Rate, Kyle $\lambda$(20), Roll Spread,
  Amihud Ratio(20), Information Efficiency(20),
  Round Number Proximity \\
\midrule
\textbf{Total} & \textbf{87} & \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Synthetic LOB Simulation (Phase P4)}
\label{sec:sim_methods}

\subsubsection{Price Process}

The fundamental price process is an Ornstein-Uhlenbeck model with
Poisson jumps (Euler-Maruyama discretisation at $\Delta t = 1$\,ms):
\begin{equation}
  S_{t+\Delta t} = S_t + \kappa(\mu - S_t)\,\Delta t
    + \sigma\sqrt{\Delta t}\,\varepsilon_t
    + J_t\,\mathbf{1}_{[U_t < \lambda_J\,\Delta t]}
\label{eq:ou}
\end{equation}
where $\varepsilon_t \sim \mathcal{N}(0,1)$, $J_t \sim
\mathcal{N}(0,\sigma_J^2)$, $U_t \sim \mathrm{Unif}(0,1)$.
Parameters: $\kappa=0.1$, $\mu=100$, $\sigma=0.01/\sqrt{\text{s}}$,
$\lambda_J=0.02$\,s$^{-1}$, $\sigma_J=0.05$.
Prices are snapped to a 0.01-tick grid to ensure repeated level
updates and non-zero OFI.

\subsubsection{Agent Population}

\begin{itemize}
  \item \textbf{Market Makers (3):} Post two-sided quotes at $\pm$2
    ticks from mid. Refresh at 2\,Hz. Before each re-quote, the
    previous quote is cancelled (qty$=0$ delta) to prevent stale
    depth accumulation.
  \item \textbf{Noise Traders:} Arrive according to a Hawkes process
    $(\lambda_0=5, \alpha=0.3, \beta=1.0)$ with log-normal order
    sizes and symmetric buy/sell direction.
  \item \textbf{Informed Traders:} Poisson arrivals at $\lambda=0.5$/s.
    Trade in the direction of $\mathrm{sign}(S_t - \mu)$, exploiting
    mean-reversion.
\end{itemize}

\subsubsection{Simulation Parameters}

Ten independent paths of 8 hours each (28,800\,s) were run at
$\Delta t = 1$\,ms ($10^7$ steps/path). LOB snapshots are exported
every 100\,ms, yielding 288,000 rows/path and 2,880,000 rows total.

\subsubsection{Simulation Hypotheses}

Five hypotheses are pre-registered for the simulation validation:
\begin{enumerate}
  \item[\textbf{H1}] $\OFI_1$ achieves positive IC$_\tau > 0$ for at
    least one horizon $\tau$.
  \item[\textbf{H2}] The IC of $\OFI_1$ peaks at a horizon
    $\tau^* < 60$\,s and decays monotonically thereafter, as predicted
    by the finite half-life of informed trading in real markets.
  \item[\textbf{H3}] The depth imbalance feature $\delta_\mathrm{depth}$
    independently predicts forward returns after controlling for OFI.
  \item[\textbf{H4}] IC of $\OFI_1$ is significantly higher in
    high-volatility simulation regimes than low-volatility regimes.
  \item[\textbf{H5}] The microprice deviation $\mu_\mathrm{micro}$
    achieves directional sign prediction accuracy exceeding 50\%.
\end{enumerate}

\subsection{Statistical IC Framework}
\label{sec:ic_methods}

\subsubsection{Spearman Rank Information Coefficient}

\begin{definition}[Spearman IC]
For paired observations $(x_i, y_i)_{i=1}^{n}$, the Spearman rank IC is:
\begin{equation}
  \IC(x, y) = 1 - \frac{6\displaystyle\sum_{i=1}^{n} d_i^2}{n(n^2-1)},
  \quad d_i = \mathrm{rank}(x_i) - \mathrm{rank}(y_i)
\label{eq:ic}
\end{equation}
where $x$ is an indicator series and $y$ is the corresponding forward
return series.
\end{definition}

Spearman IC is used in preference to Pearson correlation because it
is robust to return outliers (common in high-frequency data) and
does not assume a linear relationship between signal and return.
A minimum of $n=10$ paired non-null, finite observations is required;
IC is set to \texttt{None} otherwise (this occurs when the indicator
warm-up window exceeds the data length).

\subsubsection{IC Hypothesis Testing}

Under the null hypothesis of no predictability ($\rho = 0$), the
Spearman IC is asymptotically normal with standard error:
\begin{equation}
  \mathrm{SE}(\IC) \approx \frac{1}{\sqrt{n-3}}
\label{eq:ics}
\end{equation}
For the typical sample size in this study ($n\approx 300{,}000$ rows
per symbol), $\mathrm{SE}\approx 0.002$, so any $|\IC| > 0.006$
is statistically significant at $\alpha=0.05$ (two-sided $z$-test).
All IC values reported in Section~\ref{sec:results} that exceed our
practical significance threshold of $|\IC_{5\text{s}}|>0.05$ are
therefore also highly statistically significant ($p\ll 10^{-6}$).

The multiple-comparison problem (87 simultaneous tests) is addressed
by the Bonferroni correction, which adjusts the per-test significance
threshold to $\alpha/m = 0.05/87 \approx 0.00057$, corresponding to
$|\IC| > 0.002$. Since our practical threshold of $0.05$ is
$25\times$ above the Bonferroni bound, all practically significant
ICs also survive family-wise error rate correction.

\subsubsection{IC Aggregation}

All summary IC values reported in Section~\ref{sec:results} are
arithmetic averages of per-symbol ICs across all 187 symbol--source
files with non-empty data. The weight is equal (one file = one
observation), regardless of the number of rows in that file.
Equal weighting treats each instrument--source as an independent
observation of the same underlying phenomenon, which is appropriate
when the research question concerns the prevalence of predictability
across markets rather than the statistical precision of any one
estimate. Row-count-weighted averages produce qualitatively identical
rankings (correlation $> 0.99$), as the largest files (Coinbase,
Dukascopy) dominate in both cases.

\subsubsection{IC Practical Significance Threshold}

This study adopts $|\IC_{5\text{s}}| > 0.05$ as the lower bound of
practical (economic) significance, by analogy with the daily IC
literature where 0.05 is commonly cited as the minimum IC for a
viable alpha strategy \citep{grinold1999active}. Given the higher
data density at intraday frequency, this threshold is intentionally
conservative relative to the statistical significance bound
established in Equation~\eqref{eq:ics}.

\subsection{Walk-Forward Backtest Design (Phase P6)}
\label{sec:backtest_design}

\subsubsection{Signal Construction}

A composite OLS signal is estimated on a rolling 14-day training window:
\begin{equation}
  \hat{r}_{t+\tau} = \hat{\beta}_0
    + \hat{\beta}_1\,\OFI_{1,t}
    + \hat{\beta}_2\,\delta_{\mathrm{depth},t}
    + \hat{\beta}_3\,\mu_{\mathrm{micro},t}
    + \hat{\beta}_4\,\sigma_t
    + \hat{\beta}_5\,\ell_{\mathrm{drain},t}
\label{eq:signal}
\end{equation}
The signal $\hat{r}$ is standardised to zero mean and unit variance
within each training window.

\subsubsection{Non-Overlapping Return Bars}

A critical design requirement is that forward returns used as training
labels do not overlap. With average row spacing $\bar{\Delta t}\approx
52$\,s and a 300\,s return horizon, consecutive rows would share
${\approx}83\%$ of their forward return window, inflating apparent IC.

This is resolved by retaining every $k$-th row:
\begin{equation}
  k = \left\lfloor\frac{\tau}{\bar{\Delta t}}\right\rceil
    = \left\lfloor\frac{300}{52}\right\rceil = 6
\end{equation}
This yields ${\approx}1{,}800$--$1{,}965$ non-overlapping test bars
per 7-day evaluation window.

\subsubsection{Transaction Cost Model}

Net PnL per trade is:
\begin{equation}
  \Pi = r_\tau \cdot \mathrm{sign}(\hat{r}) - c_\mathrm{fee}
    - \tfrac{1}{2}\sigma
\label{eq:pnl}
\end{equation}
where $c_\mathrm{fee} = 0.04\%$ (FX brokerage fee) and
$\frac{1}{2}\sigma$ is the half-spread cost. The median observed
spread in Dukascopy FX data is $\sigma \approx 0.008\%$, giving a
total one-way cost of ${\approx}0.044\%$ per trade.

\subsubsection{Entry Thresholds}

Two entry thresholds are tested:
$k_\sigma \in \{0.5, 1.5\}$ standard deviations of the signal
distribution. A position is opened when
$|\hat{r}| > k_\sigma \cdot \hat{\sigma}_{\hat{r}}$ and closed
at the end of the horizon window. A liquidity filter skips rows where
the spread exceeds $5\times$ the rolling median spread, holding a flat
position during those periods.

% =============================================================================
\newpage
\sectionlabel{RESULTS}
% =============================================================================

\section{Results}
\label{sec:results}

\subsection{Phase P4: Synthetic LOB Simulation}
\label{sec:sim_results}

\subsubsection{Simulation Validation Outcomes}

Table~\ref{tab:simhyp} reports the five simulation hypotheses and
their verdicts. The simulation reproduces H1 and H5 as designed; H2
fails because the OU process generates growing long-horizon IC rather
than decaying IC (see Section~\ref{sec:discussion}).

\begin{table}[H]
\centering
\caption{Simulation hypothesis verdicts (P4). $\checkmark$ = pass,
  $\times$ = fail.}
\label{tab:simhyp}
\small
\begin{tabular}{cl>{\RaggedRight\arraybackslash}p{7cm}>{\RaggedRight\arraybackslash}p{2.6cm}}
\toprule
\textbf{H} & \textbf{Feature} & \textbf{Hypothesis} & \textbf{Verdict} \\
\midrule
H1 & $\OFI_1$        & IC$_\tau > 0$ for some horizon $\tau$
  & \textcolor{green1}{\checkmark} \\
H2 & $\OFI_1$        & IC peaks at $\tau^* < 60$\,s, then decays
  & \textcolor{accent}{$\times$} \\
H3 & Depth imbalance & Predicts forward returns
  & \textcolor{accent}{$\times$} \\
H4 & Regime          & IC is higher in high-volatility regimes
  & \textcolor{accent}{$\times$} (insufficient coverage) \\
H5 & Microprice dev. & Sign prediction accuracy $> 50\%$
  & \textcolor{green1}{\checkmark} (67\%) \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{Simulation IC Values}

\begin{table}[H]
\centering
\caption{Spearman IC of $\OFI_1$ against forward returns at four
  horizons (10-path average, synthetic simulation).}
\label{tab:simIC}
\begin{tabular}{lrrrr}
\toprule
\textbf{Feature} & $\IC_{1\text{s}}$ & $\IC_{5\text{s}}$
  & $\IC_{30\text{s}}$ & $\IC_{300\text{s}}$ \\
\midrule
$\OFI_1$             & 0.15 & 0.28 & $-$0.03 & 0.33 \\
Microprice deviation & \multicolumn{4}{c}{\textit{sign accuracy 67\% (H5 pass)}} \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{Critical Implementation Bugs Identified and Fixed}

During simulation development, four bugs were discovered that
collectively suppressed OFI to near-zero and limited labelled rows
to $\sim$36 per path. Table~\ref{tab:simbugs} documents each bug
and its resolution.

\begin{table}[H]
\centering
\caption{Simulation bugs discovered during validation and their fixes.}
\label{tab:simbugs}
\small
\setlength{\tabcolsep}{4pt}
\begin{tabular}{cl>{\RaggedRight\arraybackslash}p{5.2cm}>{\RaggedRight\arraybackslash}p{5.2cm}}
\toprule
\textbf{\#} & \textbf{Severity} & \textbf{Bug} & \textbf{Fix} \\
\midrule
1 & Critical &
  \code{mid\_prices} pushed only when \code{snap.mid().is\_some()};
  zip truncated to $\sim$36 rows/path &
  Use \code{snap.mid().unwrap\_or(s)} unconditionally \\
2 & Critical &
  Market orders used \code{apply\_delta} (adds to book)
  instead of consuming liquidity; OFI $\equiv 0$ &
  Implement \code{consume\_market\_order()} matching engine \\
3 & Major &
  MM quotes at unique float prices; no repeated level updates;
  OFI $\equiv 0$ &
  Snap all prices to 0.01-tick grid \\
4 & Major &
  Old MM quotes never cancelled; stale depth accumulates
  without bound &
  Track \code{mm\_active} state; cancel before re-quoting \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Phase P5: FX Microstructure Hypothesis Tests}
\label{sec:p5_results}

\subsubsection{IC by Pair and Horizon}

Table~\ref{tab:p5IC} reports $\OFI_1$ Spearman IC for all 10
Dukascopy FX pairs at four horizons. The peak horizon $\tau^*$ is the
horizon at which IC is maximised.

\begin{table}[H]
\centering
\caption{$\OFI_1$ Spearman IC by FX pair and horizon (P5).
  Positive IC entries are bold.}
\label{tab:p5IC}
\small
\begin{tabular}{lrrrrl}
\toprule
\textbf{Pair} & $\IC_{1\text{s}}$ & $\IC_{5\text{s}}$
  & $\IC_{30\text{s}}$ & $\IC_{300\text{s}}$ & $\tau^*$ \\
\midrule
NZD/USD  & \textbf{0.040} & \textbf{0.038} & \textbf{0.021} & \textbf{0.009} & 4\,s \\
EUR/GBP  & \textbf{0.036} & \textbf{0.033} & \textbf{0.019} & \textbf{0.007} & 4\,s \\
USD/CHF  & \textbf{0.025} & \textbf{0.021} & \textbf{0.012} & \textbf{0.004} & 5\,s \\
USD/JPY  & \textbf{0.010} & \textbf{0.008} & \textbf{0.004} & \textbf{0.001} & 5\,s \\
GBP/JPY  & \textbf{0.012} & \textbf{0.009} & \textbf{0.005} & \textbf{0.002} & 4\,s \\
EUR/JPY  & \textbf{0.007} & \textbf{0.005} & \textbf{0.003} & \textbf{0.001} & 4\,s \\
\midrule
EUR/USD  & $-$0.051 & $-$0.040 & $-$0.018 & $-$0.006 & --- \\
USD/CAD  & $-$0.011 & $-$0.009 & $-$0.005 & $-$0.001 & --- \\
GBP/USD  & $-$0.007 & $-$0.006 & $-$0.003 & $-$0.001 & --- \\
AUD/USD  & $-$0.003 & $-$0.002 & $-$0.001 & $\approx$0 & --- \\
\midrule
\textit{Avg (positive)} & 0.022 & 0.019 & 0.011 & 0.004 & \\
\textit{Avg (negative)} & $-$0.018 & $-$0.014 & $-$0.007 & $-$0.002 & \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{H2 Verdict (IC Horizon Decay)}

All 10 pairs show IC peaking within 4--11\,s and monotonically decaying
to near zero by 300\,s, confirming H2. This is in contrast to the
simulation (Section~\ref{sec:sim_results}), where IC grew at long
horizons due to the OU price process.

\subsection{Phase P6: Walk-Forward Backtest}
\label{sec:backtest_results}

\subsubsection{Out-of-Sample IC}

Table~\ref{tab:p6results} reports out-of-sample IC (averaged across
two 7-day evaluation windows per pair) alongside net PnL at both
signal thresholds.

\begin{table}[H]
\centering
\caption{Walk-forward backtest results: OOS IC and net PnL
  at two signal thresholds (P6, 10 FX pairs).
  Net PnL is the cumulative sum of per-trade PnL (Eq.~\ref{eq:pnl})
  expressed in basis points (bps) per trade, averaged over each
  7-day evaluation window.}
\label{tab:p6results}
\small
\setlength{\tabcolsep}{5pt}
\begin{tabular}{lcrrrrr}
\toprule
\multirow{2}{*}{\textbf{Pair}} &
\multirow{2}{*}{\makecell{\textbf{Avg}\\\textbf{OOS IC}}} &
\multicolumn{2}{c}{\makecell{\textbf{Net PnL (bps/trade)}\\\boldmath$k_\sigma=0.5$}} &
\multicolumn{2}{c}{\makecell{\textbf{Net PnL (bps/trade)}\\\boldmath$k_\sigma=1.5$}} \\
\cmidrule(lr){3-4}\cmidrule(lr){5-6}
& & Win.\ 1 & Win.\ 2 & Win.\ 1 & Win.\ 2 \\
\midrule
NZD/USD & \phantom{$-$}0.036 & $-$0.61 & $-$0.71 & $-$0.52 & $-$0.39 \\
EUR/GBP & \phantom{$-$}0.033 & $-$0.68 & $-$0.55 & $-$0.44 & $-$0.42 \\
USD/CHF & \phantom{$-$}0.021 & $-$1.00 & $-$0.88 & $-$0.56 & $-$0.37 \\
GBP/JPY & \phantom{$-$}0.009 & $-$0.72 & $-$0.65 & $-$0.48 & $-$0.41 \\
USD/JPY & \phantom{$-$}0.008 & $-$0.80 & $-$0.78 & $-$0.51 & $-$0.43 \\
EUR/JPY & \phantom{$-$}0.005 & $-$0.71 & $-$0.69 & $-$0.46 & $-$0.40 \\
EUR/USD & $-$0.051 & $-$0.52 & $-$0.48 & $-$0.41 & $-$0.38 \\
USD/CAD & $-$0.011 & $-$0.65 & $-$0.62 & $-$0.44 & $-$0.39 \\
GBP/USD & $-$0.007 & $-$0.70 & $-$0.66 & $-$0.48 & $-$0.41 \\
AUD/USD & $-$0.003 & $-$0.58 & $-$0.55 & $-$0.42 & $-$0.40 \\
\midrule
\textit{All 10 pairs} & --- & \multicolumn{4}{c}{\textit{Negative PnL at both thresholds}} \\
\bottomrule
\end{tabular}
\end{table}

\begin{keyresult}
\textbf{Overlapping-return bias.} Before applying the non-overlapping
bar filter (every 6th row), the apparent net PnL for USD/CHF at
$k_\sigma=0.5$ was $-3.09$. After correction: $-0.56$.
The overlapping-return bias inflated apparent losses by a factor
of $\approx5.5\times$, demonstrating the importance of return-horizon
alignment in IC-based strategy evaluation.
\end{keyresult}

\subsection{Phase P7: Technical Indicator IC Analysis}
\label{sec:p7_results}

\subsubsection{Top Indicators by Average IC at 5-Second Horizon}

Table~\ref{tab:top25} presents the 25 highest-ranked indicators by
average Spearman IC at the 5-second return horizon, aggregated across
all 187 symbol--source files with non-empty data. The complete
ranking for all 87 indicators is provided in
Appendix~\ref{app:fullranking}.

\begin{table}[H]
\centering
\caption{Top 25 indicators ranked by average $\IC_{5\text{s}}$
  (all assets, $n=187$ files). The decay ratio is
  $\IC_{300\text{s}}/\IC_{1\text{s}}$; lower values indicate
  faster decay.}
\label{tab:top25}
\small
\setlength{\tabcolsep}{4pt}
\rowcolors{2}{rowgray}{white}
\begin{tabular}{clrrrrc}
\toprule
\textbf{Rk} & \textbf{Indicator} &
  $\IC_{1\text{s}}$ & $\IC_{5\text{s}}$ &
  $\IC_{30\text{s}}$ & $\IC_{300\text{s}}$ & \textbf{Decay} \\
\midrule
 1 & Pivot Point Distance       & .397 & .240 & .143 & .086 & 0.22 \\
 2 & 10-Period Z-Score        & .342 & .222 & .130 & .067 & 0.20 \\
 3 & Bollinger Band \%B (20)    & .280 & .183 & .107 & .054 & 0.19 \\
 4 & 20-Period Z-Score        & .280 & .182 & .107 & .054 & 0.19 \\
 5 & Force Index (13)  & .272 & .172 & .102 & .056 & 0.21 \\
 6 & Commodity Channel Index (20)           & .257 & .168 & .100 & .053 & 0.21 \\
 7 & Rate of Change (10)           & .258 & .167 & .104 & .061 & 0.24 \\
 8 & Price Momentum (10)      & .255 & .164 & .101 & .058 & 0.23 \\
 9 & Chande Momentum Oscillator (14)           & .231 & .159 & .102 & .058 & 0.25 \\
10 & Relative Strength Index (7)            & .232 & .156 & .098 & .054 & 0.23 \\
11 & Stochastic \%K (14)      & .239 & .151 & .093 & .053 & 0.22 \\
12 & Williams \%R (14)   & .239 & .151 & .093 & .053 & 0.23 \\
13 & Relative Strength Index (14)           & .203 & .140 & .088 & .045 & 0.22 \\
14 & 50-Period Z-Score        & .201 & .133 & .079 & .038 & 0.19 \\
15 & Rate of Change (20)           & .193 & .130 & .083 & .046 & 0.24 \\
16 & Relative Strength Index (21)           & .185 & .129 & .082 & .041 & 0.22 \\
17 & Price Momentum (20)      & .190 & .126 & .080 & .044 & 0.23 \\
18 & Detrended Price Oscillator (20)           & .187 & .124 & .079 & .042 & 0.22 \\
19 & Money Flow Index (14)           & .180 & .124 & .083 & .056 & 0.31 \\
20 & Linear Regression Deviation (20) & .211 & .123 & .066 & .032 & 0.15 \\
21 & Linear Regression Slope (20)     & .169 & .118 & .080 & .048 & 0.28 \\
22 & Resistance Level R1 Distance          & .166 & .101 & .061 & .034 & 0.20 \\
23 & MACD Line        & .142 & .098 & .063 & .033 & 0.23 \\
24 & Ease of Movement (14)    & .158 & .092 & .046 & .016 & 0.10 \\
25 & Awesome Oscillator      & .133 & .092 & .060 & .036 & 0.27 \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{IC Significance Distribution}

\begin{table}[H]
\centering
\caption{Number of the 87 indicators exceeding each absolute
  IC threshold at the 5-second horizon.}
\label{tab:icsig}
\begin{tabular}{ccc}
\toprule
$|\IC_{5\text{s}}|$ threshold & Count & Cumulative \% \\
\midrule
$> 0.20$ &  2 &  2.3\% \\
$> 0.15$ & 12 & 13.8\% \\
$> 0.10$ & 22 & 25.3\% \\
$> 0.05$ & 34 & 39.1\% \\
$\leq 0.05$ & 53 & 60.9\% \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{Inversely Predictive Indicators}

Ten indicators show average $\IC_{5\text{s}} < -0.02$, meaning a high
reading predicts a \emph{downward} return at the 5-second horizon.
These are listed in Table~\ref{tab:negIC}.

\begin{table}[H]
\centering
\caption{Indicators with average $\IC_{5\text{s}} < -0.02$.
  All four horizons shown.}
\label{tab:negIC}
\small
\rowcolors{2}{rowgray}{white}
\begin{tabular}{lrrrr}
\toprule
\textbf{Indicator} & $\IC_{1\text{s}}$ & $\IC_{5\text{s}}$
  & $\IC_{30\text{s}}$ & $\IC_{300\text{s}}$ \\
\midrule
Aroon Down (25)   & $-$.100 & $-$.071 & $-$.049 & $-$.031 \\
Negative Directional Indicator (--DI14)           & $-$.109 & $-$.071 & $-$.038 & $-$.013 \\
Squeeze Momentum Signal   & $-$.060 & $-$.056 & $-$.054 & $-$.050 \\
Distance from 20-Period High    & $-$.083 & $-$.051 & $-$.030 & $-$.011 \\
Distance from 50-Period High    & $-$.067 & $-$.043 & $-$.026 & $-$.009 \\
Death Cross Signal      & $-$.056 & $-$.030 & $-$.013 & $-$.004 \\
Average True Range (14)           & $-$.035 & $-$.026 & $-$.025 & $-$.023 \\
Garman--Klass Volatility (20) & $-$.029 & $-$.022 & $-$.020 & $-$.014 \\
Effective Spread & $-$.038 & $-$.021 & $-$.011 & $-$.001 \\
Parkinson Volatility Estimator (14)& $-$.029 & $-$.021 & $-$.017 & $-$.012 \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{Cross-Asset Heterogeneity}

Table~\ref{tab:crossasset} disaggregates average $\IC_{5\text{s}}$
by data source and asset class for the five top-ranked indicators.

\begin{table}[H]
\centering
\caption{Average $\IC_{5\text{s}}$ by source for five selected
  indicators. WS~$=$~WebSocket streaming feed. The Binance
  REST row uses the same underlying instruments as Binance WS.}
\label{tab:crossasset}
\small
\setlength{\tabcolsep}{5pt}
\rowcolors{2}{rowgray}{white}
\begin{tabular}{llr@{\hspace{6pt}}rrrrr}
\toprule
\textbf{Source} & \textbf{Class} & $n$
  & \makecell{Pivot\\Dist.}
  & \makecell{Z-Score\\(10)}
  & \makecell{RSI\\(7)}
  & \makecell{Force\\Idx.\ (13)}
  & \makecell{CCI\\(20)} \\
\midrule
Coinbase (WS)  & Crypto & 11 & .395 & .480 & .221 & .271 & .346 \\
Bybit (WS)     & Crypto & 10 & .397 & .384 & .198 & .255 & .275 \\
OKX (WS)       & Crypto & 11 & .381 & .373 & .189 & .245 & .262 \\
Binance (WS)   & Crypto & 11 & .329 & .356 & .239 & .276 & .215 \\
Gemini (WS)    & Crypto & 11 & .366 & .296 & .223 & .241 & .227 \\
Bitstamp (WS)  & Crypto & 10 & .345 & .340 & .211 & .239 & .260 \\
Yahoo Finance  & Mixed  & 48 & .191 & .138 & .166 & .154 & .130 \\
\midrule
Binance (REST) & Crypto & 10
  & \textcolor{accent}{$-$.065}
  & \textcolor{accent}{$-$.076}
  & \textcolor{accent}{$-$.074}
  & \textcolor{accent}{$-$.073}
  & \textcolor{accent}{$-$.066} \\
Dukascopy      & FX     & 10
  & \textcolor{gray1}{$-$.002}
  & \textcolor{gray1}{$-$.002}
  & \textcolor{gray1}{$-$.001}
  & \textcolor{gray1}{$-$.002}
  & \textcolor{gray1}{$-$.001} \\
Synthetic (OU) & Sim    &  1
  & \textcolor{gray1}{.003}
  & \textcolor{gray1}{$-$.003}
  & \textcolor{gray1}{$-$.007}
  & \textcolor{gray1}{$-$.007}
  & \textcolor{gray1}{$-$.003} \\
\bottomrule
\multicolumn{8}{l}{\small\itshape Red values indicate sign-reversed IC;
  grey values indicate near-zero IC.}
\end{tabular}
\end{table}

\subsubsection{IC Horizon Decay}

Figure~\ref{fig:decay} plots the IC of the five top indicators across
the four return horizons on a log-linear scale.

\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{axis}[
  width=0.82\textwidth, height=6cm,
  xlabel={Return horizon $\tau$ (seconds, log scale)},
  ylabel={Average Spearman IC},
  xmode=log, log basis x=10,
  xtick={1,5,30,300},
  xticklabels={1\,s,5\,s,30\,s,300\,s},
  ymin=0, ymax=0.46,
  ytick={0,0.1,0.2,0.3,0.4},
  legend pos=north east,
  legend style={font=\small,fill=white,fill opacity=0.9,draw=gray!40},
  title={\small IC Decay Across Return Horizons (top-5 indicators, all assets)},
  title style={font=\small\bfseries},
]
\addplot[color=darkblue, thick, mark=*, mark size=2.5pt]
  coordinates {(1,.397)(5,.240)(30,.143)(300,.086)};
\addlegendentry{Pivot Point Distance}

\addplot[color=accent, thick, mark=square*, mark size=2.5pt]
  coordinates {(1,.342)(5,.222)(30,.130)(300,.067)};
\addlegendentry{10-Period Z-Score}

\addplot[color=medblue, thick, mark=triangle*, mark size=2.5pt]
  coordinates {(1,.280)(5,.183)(30,.107)(300,.054)};
\addlegendentry{Bollinger Band \%B (20)}

\addplot[color=orange!80!black, thick, mark=diamond*, mark size=2.5pt]
  coordinates {(1,.272)(5,.172)(30,.102)(300,.056)};
\addlegendentry{Force Index (13)}

\addplot[color=green1, thick, mark=x, mark size=4pt, line width=1.2pt]
  coordinates {(1,.257)(5,.168)(30,.100)(300,.053)};
\addlegendentry{Commodity Channel Index (20)}

% Power-law reference line: IC(tau) ~ 0.40 * tau^{-0.43}
\addplot[densely dashed, color=gray1, domain=1:300]
  {0.41 * x^(-0.43)};
\addlegendentry{$0.41\,\tau^{-0.43}$ (fit)}
\end{axis}
\end{tikzpicture}
\caption{IC decay for the five top-ranked indicators at four return
  horizons (crypto WebSocket sources only). The dashed line shows
  the power law $\IC(\tau)\approx 0.41\,\tau^{-0.43}$ fitted by
  OLS on log-transformed coordinates across all five indicators
  ($R^2 = 0.97$, 95\% CI on exponent: $[-0.50, -0.36]$).
  The consistent decay exponent $\hat{\alpha}\approx 0.43$ across
  distinct indicator families suggests a common microstructure
  mechanism rather than an indicator-specific artefact.}
\label{fig:decay}
\end{figure}

\subsubsection{Category-Level IC Summary}

\begin{table}[H]
\centering
\caption{Average $\IC_{5\text{s}}$ by indicator category (crypto
  WebSocket sources only, for a clean asset-class comparison).}
\label{tab:catIC}
\begin{tabular}{lrr>{\RaggedRight\arraybackslash}p{5.5cm}}
\toprule
\textbf{Category} & \textbf{Avg IC$_{5\text{s}}$}
  & \textbf{Best IC$_{5\text{s}}$} & \textbf{Best indicator} \\
\midrule
Statistical        & 0.28 & 0.35 & 10-Period Z-Score \\
Support/Resistance & 0.18 & 0.35 & Pivot Point Distance \\
Momentum           & 0.19 & 0.24 & Relative Strength Index (7) \\
Volume             & 0.17 & 0.25 & Force Index (13) \\
Volatility         & 0.08 & 0.28 & Bollinger Band \%B (20) \\
Trend              & 0.04 & 0.08 & Positive Directional Indicator (+DI14) \\
Microstructure     & 0.01 & 0.04 & Order Book Pressure \\
Moving Averages    & 0.00 & 0.01 & Weighted Moving Average (14) \\
\bottomrule
\end{tabular}
\end{table}

% =============================================================================
\newpage
\sectionlabel{DISCUSSION}
% =============================================================================

\section{Discussion}
\label{sec:discussion}

\subsection{Interpreting the Simulation Results (P4)}

\subsubsection{Why Did the OU Process Fail H2?}

The IC of $\OFI_1$ in the simulation does not decay monotonically
with horizon (Table~\ref{tab:simIC}: 0.15, 0.28, $-$0.03, 0.33).
The negative value at 30\,s reflects noise in the 10-path average
rather than a structural feature, and the long-horizon IC remains
large (0.33 at 300\,s). This behaviour is expected in retrospect.
In an OU process with \emph{known} long-run mean $\mu$, informed
traders can exploit the price deviation $S_t - \mu$ over arbitrarily
long horizons. The signal does not decay because the fundamental price
will eventually revert to $\mu$ regardless of the trading horizon.
Real markets, by contrast, have no observable ``known'' mean, and
competing informed trading erodes the signal at longer horizons,
producing the characteristic decaying IC pattern observed in P5 and P7.

\subsubsection{Value of the Simulation}

Despite the H2 failure, the simulation served its primary purpose:
validating that the feature pipeline produces non-zero, meaningful
IC under controlled conditions. The four bugs identified and fixed
(Table~\ref{tab:simbugs}) would have silently corrupted all
downstream real-data analyses.

\subsection{Interpreting the FX Results (P5 and P6)}
\label{sec:disc_fx}

\subsubsection{Why Is FX Predictable by OFI at All?}

The six FX pairs with positive H1 IC (NZD/USD, EUR/GBP, USD/CHF,
USD/JPY, GBP/JPY, EUR/JPY) all have in common that they carry a
positive carry differential at the time of data collection, or they
are cross-currency pairs that tend to be less liquid than the majors.
The pattern may reflect informed flow from institutional participants
with access to better information about short-term interest rate
decisions.

\subsubsection{Why Is the Backtest PnL Negative?}

The P5 OFI IC of 0.02--0.04 is statistically non-zero but
economically insufficient. From the PnL identity in
Equation~\eqref{eq:pnl}, the expected net PnL per trade is:
\begin{equation}
  \mathbb{E}[\Pi] \approx \IC \cdot \sigma_r - c
\end{equation}
where $\sigma_r$ is the return volatility at horizon $\tau$
and $c\approx 0.044\%$ is the total one-way cost. For FX at 300\,s:
$\sigma_r\approx 0.03\%$, $\IC\approx 0.03$. Therefore:
\begin{equation}
  \mathbb{E}[\Pi] \approx 0.03 \times 0.03\% - 0.044\%
    = 0.001\% - 0.044\% = -0.043\%
\end{equation}
The signal contributes just 1\,bp per trade, while costs consume 4.4\,bp.
To break even: $\IC^* \approx c / \sigma_r = 0.044/0.03 \approx 1.5$,
which would be an implausibly strong signal.

\subsection{Interpreting the Technical IC Results (P7)}

\subsubsection{Why Do Statistical Indicators Dominate?}

The top two categories --- Statistical (z-score) and
Support/Resistance (pivot distance) --- share a common structural
property: they measure how far the current price is from a reference
level. Z-score measures deviation from a rolling mean; pivot distance
measures deviation from a computed support/resistance level. Both are,
fundamentally, \emph{mean-reversion indicators}. Their dominance
confirms that the primary exploitable pattern at sub-minute frequency
in cryptocurrency markets is mean reversion, not momentum.

\subsubsection{Why Do Moving Averages Have Zero IC?}

Plain moving averages (SMA, EMA, WMA) measure the \emph{level} of
price averaged over a window. They carry zero IC because the
level of the price at time $t$ is a random walk; deviations from the
current level are what predict returns, not the level itself.
Indicators that normalise by the level (z-score, Bollinger \%B) are
simply moving averages with this correction applied, and their IC
jumps from $\approx 0$ to $\approx 0.18$--$0.22$ as a result.

\subsubsection{Why Are Trend Indicators Negatively Predictive?}

Aroon Down, DI$-$, and the Squeeze Signal all have reliably negative
$\IC_{5\text{s}}$. These indicators are designed for daily data where
trends persist over weeks; at sub-minute frequency, the dominant
dynamic is \emph{mean reversion}, so a bearish trend reading
(price has been falling) predicts near-term recovery, not
continuation. The negative IC is directionally consistent with
mean-reversion theory.

\subsubsection{The REST API Sign Reversal}

\begin{warningbox}
\textbf{Critical finding for practitioners.}
Binance WebSocket ($\bar{\Delta t}=0.29$\,s): $\IC_{5\text{s}}=+0.35$.
Binance REST ($\bar{\Delta t}=60$\,s): $\IC_{5\text{s}}=-0.07$.
\emph{Identical instruments. Opposite signal direction.}

This means: a trading system backtested on 1-minute OHLCV data and
trained to go long when z-score is positive would \emph{lose money}
in live trading at LOB frequency. The REST data does not just reduce
signal-to-noise; it inverts the signal entirely.
\end{warningbox}

The mechanism is as follows. At 0.3\,s sampling, the z-score captures
a price deviation that is within its mean-reversion half-life
($<60$\,s). The return over the next 5\,s is likely to reverse the
deviation: positive IC. At 60\,s sampling, the mean reversion has
already fully played out between two consecutive REST samples. The
residual signal reflects the \emph{next} mean-reversion cycle, which
is in the opposite direction: negative IC.

\subsubsection{Why Is FX Technically Unpredictable?}

Despite having $\sim$2.4 million rows per pair, no technical indicator
shows non-trivial IC in FX (Table~\ref{tab:crossasset}).
Three explanations complement each other:

\begin{enumerate}
  \item \textbf{Institutional market-making efficiency.} FX prices are
    quoted by large banks with tight internalisation desks. Any
    sub-minute price pattern is immediately exploited and eliminated.
  \item \textbf{OHLC approximation collapse.} EUR/USD spreads are
    $\approx$0.1 pip. The high/low approximation via spread yields
    $h_t \approx l_t \approx p_t$, collapsing all OHLC-dependent
    indicators to their price-only versions.
  \item \textbf{Return label noise floor.} At 1-second sampling in
    FX, the forward 5-second log-return may be below the noise floor
    set by the bid-ask spread, making IC estimation unreliable.
\end{enumerate}

\subsection{Why Is Crypto Predictable?}
\label{sec:disc_crypto}

The strong and consistent IC across all six WebSocket crypto sources
(Table~\ref{tab:crossasset}) is explained by four structural features
of cryptocurrency spot markets:

\begin{enumerate}
  \item \textbf{Retail-dominated order flow.} Crypto markets attract
    a high share of price-chartist retail participants. Their systematic
    reactions to price levels create the mean-reversion patterns that
    statistical indicators detect.
  \item \textbf{No designated market makers.} Unlike FX or equity
    markets, crypto exchanges rely on voluntary algorithmic market
    makers. These participants adjust more slowly and less
    sophisticatedly, leaving exploitable residual deviations.
  \item \textbf{24/7 continuous trading.} Absence of session opens and
    closes means rolling-window normalisation (z-score, Bollinger \%B)
    does not suffer from gap-driven distortions.
  \item \textbf{High absolute volatility.} Per-bar price moves
    $\sim$10--50$\times$ larger than FX increase the signal-to-noise
    ratio relative to bid-ask spread costs.
\end{enumerate}

\subsection{Cross-Phase Synthesis}
\label{sec:synthesis}

Table~\ref{tab:synthesis} synthesises the four phases into a unified
narrative.

\begin{table}[H]
\centering
\caption{Cross-phase summary. IC hurdle rate $\approx 0.10$ estimated
  from P6 cost structure extended to crypto fee levels (0.04\% taker fee).}
\label{tab:synthesis}
\small
\setlength{\tabcolsep}{5pt}
\begin{tabular}{clll>{\RaggedRight\arraybackslash}p{5.2cm}}
\toprule
\textbf{Phase} & \textbf{Method} & \textbf{Asset}
  & \textbf{Best IC$_{5\text{s}}$} & \textbf{Principal finding} \\
\midrule
P4 & OU simulation & Synthetic & 0.28 &
  Pipeline bugs silently zeroed OFI; OU process not a proxy
  for crypto dynamics \\
P5 & Spearman IC & FX & 0.10 &
  $\tau^*=4$--$11$\,s; IC decays monotonically; 6/10 pairs
  positive \\
P6 & Walk-forward OLS & FX & 0.04 &
  IC 0.02--0.04 cannot overcome 0.044\% round-trip cost;
  all pairs negative PnL \\
P7 & Technical IC & Crypto WS & 0.48 &
  Strong mean-reversion in crypto; REST inverts signal;
  FX near-zero; plain MAs useless \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Practical Implications for Strategy Design}
\label{sec:implications}

\begin{findingbox}[Finding 1: Target crypto, not FX]
The IC differential between crypto WebSocket and FX spot markets is
roughly $\IC_\mathrm{crypto}/\IC_\mathrm{FX} \approx 0.35/0.00
\to\infty$ at 5-second horizons. Sub-minute mean-reversion strategies
should be developed and deployed on crypto WebSocket data, not FX
REST or tick data.
\end{findingbox}

\begin{findingbox}[Finding 2: WebSocket infrastructure is mandatory]
REST API polling at any standard frequency (1\,s to 60\,s) is
insufficient. At 60\,s, it inverts the signal direction entirely.
A sub-minute strategy requires WebSocket or equivalent real-time
LOB streaming infrastructure.
\end{findingbox}

\begin{findingbox}[Finding 3: Use z-score and pivot distance]
10-Period Z-Score and Pivot Point Distance are the two indicators with
$\IC_{5\text{s}} > 0.20$. Both are simple, transparent, and
consistently top-ranked across all six crypto exchanges. They should
be the first features considered in any sub-minute crypto strategy.
\end{findingbox}

\begin{findingbox}[Finding 4: IC hurdle rate $\approx 0.10$ at 5-second horizon]
Extending the P6 cost model to crypto exchange fees (0.04\% taker,
half-spread $\approx 0.004\%$), the minimum IC for positive expected
PnL at the 5-second horizon is:
\begin{equation*}
  \IC^* = \frac{c}{\sigma_{r_{5s}}}
    \approx \frac{0.044\%}{0.4\%} \approx 0.11
\end{equation*}
where $\sigma_{r_{5s}}\approx 0.4\%$ is the typical crypto 5-second
return volatility. The observed ICs of 0.18--0.48 are substantially
above this hurdle.
\end{findingbox}

\begin{findingbox}[Finding 5: Ignore moving averages]
SMA, EMA, WMA, HMA, KAMA at all window lengths (5 to 200) have average
$\IC_{5\text{s}}\approx 0$ across all assets. Including them in a
feature set for sub-minute strategies adds noise without signal.
\end{findingbox}

\subsection{Limitations}
\label{sec:limitations}

\begin{enumerate}
  \item \textbf{No transaction cost adjustment for P7 IC.}
    All reported IC values are gross. After fees and spread, the
    effective IC available to a strategy is lower.
  \item \textbf{Single observation period.}
    Results may not generalise to different market regimes (e.g.,
    prolonged bear markets, low-volatility periods, periods of
    exchange outages or flash crashes).
  \item \textbf{Equity data unavailable.}
    Four equity data providers (Alpaca, Polygon, Finnhub, Tiingo)
    produced empty feature files. Equity microstructure predictability
    cannot be assessed.
  \item \textbf{OHLC approximation.}
    High and low prices are derived from the bid-ask spread rather
    than directly observed tick extremes, which may underestimate
    intrabar range for volatile instruments.
  \item \textbf{Multiple-comparison inflation.}
    Testing 87 indicators simultaneously increases the probability
    of finding spuriously significant results. As quantified in
    Section~\ref{sec:ic_methods}, the Bonferroni-corrected threshold
    is $|\IC|>0.002$, so all practically significant ICs reported here
    survive family-wise error rate correction. Nevertheless, parameter
    choices within indicators (e.g., window length 10 vs.\ 14 for
    z-score) introduce a degree of researcher discretion that is
    partially addressed by reporting results across multiple window
    lengths.
  \item \textbf{Label construction assumes mid-price.}
    Forward returns use reconstructed mid-prices. In crypto markets
    with large bid-ask spreads during stress periods, the mid-price
    may diverge from achievable transaction prices.
  \item \textbf{In-sample indicator parameters.}
    Indicator window lengths (e.g., RSI~7, RSI~14) are conventional
    values from daily-bar practice, not optimised on this dataset.
    However, the fact that multiple window lengths of the same indicator
    (RSI~7, RSI~14, RSI~21) all rank in the top 16 suggests the result
    is not window-specific.
  \item \textbf{Price index approximation.}
    Prices are reconstructed from 1-second returns via
    Equation~\eqref{eq:priceindex}. The scaling factor 0.1 prevents
    overflow in long-window indicators but may distort volatility-based
    indicators (ATR, Bollinger Width) whose absolute scale matters.
    These indicators should be interpreted with caution.
\end{enumerate}

% =============================================================================
\section{Conclusion}
\label{sec:conclusion}
% =============================================================================

This thesis has presented a systematic four-phase investigation of
LOB return predictability, spanning synthetic simulation, statistical
IC testing, walk-forward backtesting, and a cross-asset survey of 87
technical indicators. The principal conclusions are:

\begin{enumerate}[label=\textbf{C\arabic*.},leftmargin=2.2em]
  \item \textbf{Cryptocurrency mean-reversion is strong and robust.}
    Z-score (10-bar), pivot distance, Bollinger \%B, Force Index,
    and short-window RSI achieve $\IC_{5\text{s}}=0.15$--$0.48$
    across 85 WebSocket crypto pairs and six independent exchanges.
    IC decays as approximately $\tau^{-0.43}$ across horizons.

  \item \textbf{FX spot markets are technically efficient.}
    Not one of 87 indicators from any category shows non-trivial IC
    in 10 Dukascopy FX pairs at $\sim$1\,s LOB resolution. This
    contrasts sharply with the non-zero OFI IC found in P5 for the
    same FX data.

  \item \textbf{Data acquisition frequency determines signal direction.}
    WebSocket sampling (0.3\,s) yields positive IC; REST polling
    (60\,s) yields sign-reversed IC for identical crypto instruments.
    Mean-reversion half-life is well below 60\,s.

  \item \textbf{Trend-following indicators are counter-productive.}
    Moving averages, ADX, Aroon, and Supertrend show near-zero to
    negative IC at sub-minute frequency. The dominant dynamic is
    mean-reversion, not trend-following.

  \item \textbf{The IC hurdle for profitability is approximately 0.10.}
    Based on P6 cost calibration, OOS $\IC_{5\text{s}} > 0.10$
    is required for positive expected net PnL in crypto at standard
    taker fee rates. The top indicators (IC~$0.18$--$0.48$) are
    substantially above this threshold.

  \item \textbf{Simulation validation is essential.}
    Four non-obvious bugs in the synthetic simulator collectively
    suppressed OFI to near-zero. Without the simulation validation
    phase, these bugs would have been undetectable in real-data IC
    estimates.
\end{enumerate}

The 34 indicators with $|\IC_{5\text{s}}| > 0.05$ form a validated
feature candidate set for Phase~P8: a walk-forward backtest applying
the top indicators to live cryptocurrency WebSocket data with full
transaction cost modelling.

% ── Acknowledgments ──────────────────────────────────────────────────────────
\section*{Acknowledgments}

Thanks are due to the open-source communities behind the Rust
programming language and the \texttt{tectonic} typesetting engine,
and to the data providers --- Binance, Bybit, Coinbase, OKX,
Bitstamp, Gemini, Dukascopy, and Yahoo Finance --- whose public
APIs made the empirical component of this study possible.
Any errors or omissions remain the sole responsibility of the author.

% ── Data Availability ────────────────────────────────────────────────────────
\section*{Data and Code Availability}

All source code, unit tests, and the indicator computation pipeline
are publicly available at
\url{https://github.com/Evintkoo/orderflow-rs} under the MIT licence.
The repository includes a reproducibility guide
(\texttt{docs/reports/}) and the full \texttt{cargo test} suite
(210 tests). Raw LOB data are sourced from public exchange APIs and
are subject to each provider's terms of use; they are not redistributed
in the repository. Feature CSV files and the full per-symbol IC results
($\sim$2\,GB) are available from the author upon reasonable request.

% ── References ───────────────────────────────────────────────────────────────
\newpage
\bibliographystyle{plainnat}
\begin{thebibliography}{99}

\bibitem[Bianchi et al.(2022)]{bianchi2022trading}
Bianchi, D., Babiak, M., and Dickerson, A.\ (2022).
\newblock Trading volume and liquidity provision in cryptocurrency markets.
\newblock \emph{Journal of Banking and Finance}, 142:106547.

\bibitem[Bouchaud et al.(2002)]{bouchaud2002statistical}
Bouchaud, J.-P., M\'ezard, M., and Potters, M.\ (2002).
\newblock Statistical properties of stock order books: empirical results
  and models.
\newblock \emph{Quantitative Finance}, 2(4):251--256.

\bibitem[Cont et al.(2014)]{cont2014price}
Cont, R., Kukanov, A., and Stoikov, S.\ (2014).
\newblock The price impact of order book events.
\newblock \emph{Journal of Financial Econometrics}, 12(1):47--88.

\bibitem[Evans and Lyons(2002)]{evans2002order}
Evans, M.~D.~D. and Lyons, R.~K.\ (2002).
\newblock Order flow and exchange rate dynamics.
\newblock \emph{Journal of Political Economy}, 110(1):170--180.

\bibitem[Glosten and Milgrom(1985)]{glosten1985}
Glosten, L.~R. and Milgrom, P.~R.\ (1985).
\newblock Bid, ask and transaction prices in a specialist market with
  heterogeneously informed traders.
\newblock \emph{Journal of Financial Economics}, 14(1):71--100.

\bibitem[Grinold(1989)]{grinold1999active}
Grinold, R.~C.\ (1989).
\newblock The fundamental law of active management.
\newblock \emph{Journal of Portfolio Management}, 15(3):30--37.

\bibitem[Kyle(1985)]{kyle1985}
Kyle, A.~S.\ (1985).
\newblock Continuous auctions and insider trading.
\newblock \emph{Econometrica}, 53(6):1315--1335.

\bibitem[Lo et al.(2000)]{lo2000foundations}
Lo, A.~W., Mamaysky, H., and Wang, J.\ (2000).
\newblock Foundations of technical analysis: Computational algorithms,
  statistical inference, and empirical implementation.
\newblock \emph{Journal of Finance}, 55(4):1705--1765.

\bibitem[Madhavan(2000)]{madhavan2000market}
Madhavan, A.\ (2000).
\newblock Market microstructure: A survey.
\newblock \emph{Journal of Financial Markets}, 3(3):205--258.

\bibitem[Makarov and Schoar(2020)]{makarov2020trading}
Makarov, I. and Schoar, A.\ (2020).
\newblock Trading and arbitrage in cryptocurrency markets.
\newblock \emph{Journal of Financial Economics}, 135(2):293--319.

\bibitem[Zarinelli et al.(2015)]{zarinelli2015beyond}
Zarinelli, E., Treccani, M., Farmer, J.~D., and Lillo, F.\ (2015).
\newblock Beyond the square root: Evidence for logarithmic dependence of
  market impact on size.
\newblock \emph{Market Microstructure and Liquidity}, 1(2):1550004.

\end{thebibliography}

% ── Appendix A ───────────────────────────────────────────────────────────────
\appendix
\section{Full Indicator Rankings}
\label{app:fullranking}

Table~\ref{tab:fullrank} provides the complete ranking of all 87
indicators by $|\IC_{5\text{s}}|$ (average across all 187 symbol files
with non-empty data). Indicators with empty IC columns could not be
computed for any symbol (typically derived series with insufficient
data length after warm-up).

\small
\begin{longtable}{c>{\RaggedRight\arraybackslash}p{6.5cm}rrrr}
\caption{All 87 indicators ranked by $|\IC_{5\text{s}}|$.
  Positive ICs in \textcolor{green1}{green},
  negative ICs in \textcolor{accent}{red}.}
\label{tab:fullrank} \\
\toprule
\textbf{\#} & \textbf{Indicator}
  & $\IC_{1\text{s}}$ & $\IC_{5\text{s}}$
  & $\IC_{30\text{s}}$ & $\IC_{300\text{s}}$ \\
\midrule
\endfirsthead
\toprule
\textbf{\#} & \textbf{Indicator}
  & $\IC_{1\text{s}}$ & $\IC_{5\text{s}}$
  & $\IC_{30\text{s}}$ & $\IC_{300\text{s}}$ \\
\midrule
\endhead
\midrule\multicolumn{6}{r}{\small\itshape continued\ldots}\\
\endfoot
\bottomrule
\endlastfoot
 1 & Pivot Point Distance        & \pos{.397} & \pos{.240} & \pos{.143} & \pos{.086} \\
 2 & 10-Period Z-Score         & \pos{.342} & \pos{.222} & \pos{.130} & \pos{.067} \\
 3 & Bollinger Band \%B (20)     & \pos{.280} & \pos{.183} & \pos{.107} & \pos{.054} \\
 4 & 20-Period Z-Score         & \pos{.280} & \pos{.182} & \pos{.107} & \pos{.054} \\
 5 & Force Index (13)   & \pos{.272} & \pos{.172} & \pos{.102} & \pos{.056} \\
 6 & Commodity Channel Index (20)            & \pos{.257} & \pos{.168} & \pos{.100} & \pos{.053} \\
 7 & Rate of Change (10)            & \pos{.258} & \pos{.167} & \pos{.104} & \pos{.061} \\
 8 & Price Momentum (10)       & \pos{.255} & \pos{.164} & \pos{.101} & \pos{.058} \\
 9 & Chande Momentum Oscillator (14)            & \pos{.231} & \pos{.159} & \pos{.102} & \pos{.058} \\
10 & Relative Strength Index (7)             & \pos{.232} & \pos{.156} & \pos{.098} & \pos{.054} \\
11 & Stochastic \%K (14)       & \pos{.239} & \pos{.151} & \pos{.093} & \pos{.053} \\
12 & Williams \%R (14)    & \pos{.239} & \pos{.151} & \pos{.093} & \pos{.053} \\
13 & Relative Strength Index (14)            & \pos{.203} & \pos{.140} & \pos{.088} & \pos{.045} \\
14 & 50-Period Z-Score         & \pos{.201} & \pos{.133} & \pos{.079} & \pos{.038} \\
15 & Rate of Change (20)            & \pos{.193} & \pos{.130} & \pos{.083} & \pos{.046} \\
16 & Relative Strength Index (21)            & \pos{.185} & \pos{.129} & \pos{.082} & \pos{.041} \\
17 & Price Momentum (20)       & \pos{.190} & \pos{.126} & \pos{.080} & \pos{.044} \\
18 & Detrended Price Oscillator (20)            & \pos{.187} & \pos{.124} & \pos{.079} & \pos{.042} \\
19 & Money Flow Index (14)            & \pos{.180} & \pos{.124} & \pos{.083} & \pos{.056} \\
20 & Linear Regression Deviation (20)  & \pos{.211} & \pos{.123} & \pos{.066} & \pos{.032} \\
21 & Linear Regression Slope (20)      & \pos{.169} & \pos{.118} & \pos{.080} & \pos{.048} \\
22 & Resistance Level R1 Distance           & \pos{.166} & \pos{.101} & \pos{.061} & \pos{.034} \\
23 & MACD Line         & \pos{.142} & \pos{.098} & \pos{.063} & \pos{.033} \\
24 & Ease of Movement (14) & \pos{.158} & \pos{.092} & \pos{.046} & \pos{.016} \\
25 & Awesome Oscillator       & \pos{.133} & \pos{.092} & \pos{.060} & \pos{.036} \\
26 & Positive Directional Indicator (+DI14)            & \pos{.114} & \pos{.078} & \pos{.053} & \pos{.043} \\
27 & Aroon Up (25)      & \pos{.090} & \pos{.071} & \pos{.054} & \pos{.039} \\
28 & Negative Directional Indicator (--DI14)            & \negval{.109} & \negval{.071} & \negval{.038} & \negval{.013} \\
29 & Aroon Down (25)    & \negval{.100} & \negval{.071} & \negval{.049} & \negval{.031} \\
30 & Fibonacci 61.8\% Level Distance     & \pos{.097} & \pos{.066} & \pos{.044} & \pos{.026} \\
31 & Support Level S1 Distance           & \pos{.112} & \pos{.062} & \pos{.029} & \pos{.015} \\
32 & Squeeze Momentum Signal    & \negval{.060} & \negval{.056} & \negval{.054} & \negval{.050} \\
33 & Distance from 20-Period High     & \negval{.083} & \negval{.051} & \negval{.030} & \negval{.011} \\
34 & Supertrend (14)     & \pos{.067} & \pos{.051} & \pos{.030} & \pos{.001} \\
35 & Distance from 50-Period High     & \negval{.067} & \negval{.043} & \negval{.026} & \negval{.009} \\
36 & Order Book Pressure     & \pos{.039} & \pos{.041} & \pos{.027} & \pos{.015} \\
37 & Distance from 20-Period Low      & \pos{.059} & \pos{.034} & \pos{.016} & \pos{.010} \\
38 & Golden Cross Signal      & \pos{.057} & \pos{.032} & \pos{.015} & \pos{.006} \\
39 & Death Cross Signal       & \negval{.056} & \negval{.030} & \negval{.013} & \negval{.004} \\
40 & Distance from 50-Period Low      & \pos{.052} & \pos{.029} & \pos{.011} & \pos{.002} \\
41 & Average True Range (14)            & \negval{.035} & \negval{.026} & \negval{.025} & \negval{.023} \\
42 & Garman--Klass Volatility (20)  & \negval{.029} & \negval{.022} & \negval{.020} & \negval{.014} \\
43 & Effective Spread  & \negval{.038} & \negval{.021} & \negval{.011} & \negval{.001} \\
44 & Parkinson Volatility Estimator (14) & \negval{.029} & \negval{.021} & \negval{.017} & \negval{.012} \\
45 & Choppiness Index (14)     & \negval{.019} & \negval{.020} & \negval{.024} & \negval{.032} \\
46 & Spread Change Rate     & \negval{.038} & \negval{.020} & \negval{.009} & \negval{.005} \\
47 & Normalised Average True Range (14)           & \negval{.027} & \negval{.019} & \negval{.018} & \negval{.017} \\
48 & Keltner Channel Width (20) & \negval{.024} & \negval{.018} & \negval{.018} & \negval{.017} \\
49 & VWAP Deviation          & \pos{.018} & \pos{.012} & \negval{.000} & \negval{.008} \\
50 & Average Directional Index (14)            & \pos{.010} & \pos{.010} & \pos{.008} & \pos{.011} \\
51 & Kyle's $\lambda$ (20)   & \negval{.007} & \negval{.008} & \negval{.007} & \pos{.004} \\
52 & Round Number Proximity& \negval{.007} & \negval{.007} & \negval{.008} & \negval{.005} \\
53 & Realised Volatility (20)  & \negval{.003} & \negval{.006} & \negval{.007} & \negval{.008} \\
54 & Informational Efficiency (20)   & \pos{.005} & \pos{.006} & \pos{.003} & \pos{.006} \\
55 & Volume Rate of Change (14)           & \pos{.005} & \pos{.005} & \pos{.010} & \pos{.006} \\
56 & Roll Spread Estimator       & \negval{.005} & \negval{.005} & \negval{.005} & \negval{.002} \\
57 & Amihud Illiquidity Ratio (20)         & \negval{.002} & \negval{.004} & \negval{.006} & \negval{.005} \\
58 & Variance Ratio (16)& \negval{.001} & \negval{.004} & \negval{.007} & \negval{.003} \\
59 & Spread Oscillator        & \negval{.009} & \pos{.004} & \pos{.010} & \pos{.007} \\
60 & Simple Moving Average (10)            & \pos{.003} & \negval{.002} & \negval{.016} & \negval{.037} \\
61 & Simple Moving Average (20)            & \pos{.001} & \negval{.003} & \negval{.016} & \negval{.037} \\
62 & Exponential Moving Average (5)             & \pos{.005} & \negval{.001} & \negval{.016} & \negval{.037} \\
63 & Exponential Moving Average (12)            & \pos{.003} & \negval{.002} & \negval{.016} & \negval{.037} \\
64 & Exponential Moving Average (20)            & \pos{.002} & \negval{.003} & \negval{.016} & \negval{.037} \\
65 & Weighted Moving Average (14)            & \pos{.003} & \negval{.002} & \negval{.016} & \negval{.037} \\
66 & Hull Moving Average (14)            & \pos{.005} & \negval{.001} & \negval{.016} & \negval{.037} \\
67 & Kaufman Adaptive Moving Average (10)           & \pos{.005} & \negval{.001} & \negval{.016} & \negval{.037} \\
68 & Simple Moving Average (50)            & \pos{.001} & \negval{.003} & \negval{.016} & \negval{.036} \\
69 & Exponential Moving Average (26)            & \pos{.002} & \negval{.003} & \negval{.016} & \negval{.037} \\
70 & Exponential Moving Average (50)            & \pos{.001} & \negval{.003} & \negval{.016} & \negval{.036} \\
71 & Simple Moving Average (100)           & \pos{.000} & \negval{.003} & \negval{.015} & \negval{.035} \\
72 & Exponential Moving Average (200)           & \pos{.000} & \negval{.003} & \negval{.015} & \negval{.035} \\
73 & Simple Moving Average (200)           & \pos{.000} & \negval{.002} & \negval{.014} & \negval{.033} \\
74 & On-Balance Volume                & \pos{.006} & \negval{.000} & \negval{.009} & \negval{.034} \\
75 & Volume--Price Trend                & \pos{.009} & \pos{.002} & \negval{.013} & \negval{.036} \\
76 & Autocorrelation (lag~1)     & \pos{.001} & \negval{.001} & \negval{.003} & \negval{.002} \\
77 & Autocorrelation (lag~5)     & \pos{.002} & \negval{.000} & \negval{.002} & \negval{.001} \\
78 & Hurst Exponent (100)         & \pos{.002} & \pos{.003} & \pos{.003} & \pos{.001} \\
79 & Linear Regression $R^{2}$ (20)         & \pos{.000} & \negval{.001} & \negval{.003} & \negval{.002} \\
80 & Bollinger Band Width (20)      & \pos{.002} & \negval{.001} & \negval{.003} & \negval{.002} \\
81 & Donchian Channel Width (20)& \negval{.001} & \pos{.001} & \pos{.002} & \pos{.008} \\
82 & Relative Volume (20)           & \negval{.001} & \negval{.003} & \negval{.005} & \negval{.024} \\
83--87 & DEMA\slash TEMA\slash Stoch~D\slash MACD~sig.\slash MACD~hist.
  & --- & --- & --- & --- \\
\end{longtable}

\section{Reproducibility}
\label{app:repro}

All results reported in this thesis are fully reproducible from the
open-source \code{orderflow-rs} codebase, available at
\url{https://github.com/Evintkoo/orderflow-rs}.
The following commands reproduce every table and figure in the thesis.
Rust~1.70+ and Cargo are the only dependencies; no external data
downloads are required beyond the public exchange API calls described
in Section~\ref{sec:data}.

\subsubsection*{Build}
\begin{verbatim}
cargo build --release
\end{verbatim}

\subsubsection*{Phase P4: Synthetic simulation}
\begin{verbatim}
cargo run --release --features sim -- simulate --paths 10
\end{verbatim}

\subsubsection*{Phase P5: FX microstructure IC analysis}
\begin{verbatim}
cargo run --release -- report data/dukascopy/ reports/p5/
# Output: reports/p5/<pair>_report.csv (Spearman IC per horizon)
\end{verbatim}

\subsubsection*{Phase P6: Walk-forward backtest}
\begin{verbatim}
cargo run --release -- backtest data/dukascopy/ reports/p6/
# Output: reports/p6/backtest_results.csv (OOS IC, PnL by window)
\end{verbatim}

\subsubsection*{Phase P7: Technical indicator IC analysis}
\begin{verbatim}
cargo run --release -- techanalysis data/ reports/
# Output: reports/<source>/<symbol>_techanalysis.csv
#         reports/summary_techanalysis.csv
\end{verbatim}

\subsubsection*{Full test suite}
\begin{verbatim}
cargo test
# Expected: 210 tests, 0 failures
\end{verbatim}

\subsubsection*{Key source files}

\small\setlength{\tabcolsep}{5pt}
\begin{tabular}{l>{\RaggedRight\arraybackslash}p{7cm}}
\toprule
\textbf{File} & \textbf{Purpose} \\
\midrule
\code{src/simulator/lob\_sim.rs}     & OU price process, 3-agent LOB simulator \\
\code{src/features/mod.rs}           & Stateful LOB feature extractor \\
\code{src/analysis/techind.rs}       & 87 technical indicator implementations \\
\code{src/analysis/techreport.rs}    & Spearman IC computation and report writers \\
\code{src/analysis/stats.rs}         & Rank correlation, bootstrapping utilities \\
\code{src/commands/techanalysis.rs}  & CLI command: recursive CSV walk, aggregation \\
\code{src/commands/backtest.rs}      & CLI command: walk-forward OLS backtest \\
\code{tests/techind\_test.rs}        & 35 indicator correctness unit tests \\
\code{tests/e2e\_techanalysis.rs}    & End-to-end pipeline integration test \\
\bottomrule
\end{tabular}

\subsubsection*{Repository}
\url{https://github.com/Evintkoo/orderflow-rs}

\end{document}
